Staged Abstract Interpreters

### 2018-10-21 paper/10_intro.tex
misc

2. Multi-stage programming is widely used in high performance computation.
Precise whole-program analysis can be very slow, how to optimize it systematically/mechanically?
bridging the gap between designing sound analyses and implementing efficient analyses.

@@

3. analyzing modern programs with large libraries are expensive, we need to a way to create
summaries of libraries so that we can reuse them.

>>>>

2. Multi-stage programming is widely used in high performance computation.
Precise whole-program analysis can be very slow, how to optimize it systematically/mechanically?
bridging the gap between designing sound analyses and implementing efficient analyses.
partial evaluation on program analyzers is not a new idea, remove the interpretive overhead of repetively 
traversing the abstract syntax tree.
we revisit this approach from a more recent perspective by combining general abstract interpreters
and multi-stage programming.

@@

3. analyzing modern programs with large libraries are expensive, repetitively analyze the part of library,
modularity as in compilers, we need to a way to create summaries of libraries so that we can reuse them,
remove redundant analyzing of libraries.
